Classical Simulation of Quantum Error Correction in a Fibonacci Anyon Code

### 2016-10-25 resubmit/Response.txt

We thank the editors for their consideration and the referees for their comments. Our manuscript has been significantly revised in response to the concerns of the referees, and we have added a significant supplementary text to flesh out the details of the simulation algorithm as suggested. We believe that we have now addressed the referees comments sufficiently to warrant reconsideration for publication. More specific responses to each referee are as follows:

@@

Referee A:

We thank the referee for their generous comments about our manuscript. The referee's main concern is that the details of our simulation algorithm were not presented in enough detail to judge our manuscript's validity, and states that after overcoming this problem, our manuscript will be "an excellent contribution to PRL". We have revised the main text to clarify several points, but our primary remedy to this deficiency is by appending supplementary material that we hope addresses the referee's concerns. Additionally, one of the authors has recently posted a separate manuscript to the arXiv (1610.05384) that details some of the theoretical underpinnings of our simulation.

In response to the referee's specific concerns:
1) As suggested by the referee, we have included supplementary material that significantly expands the discussion of the simulation algorithm, as well as providing a reference to a new manuscript that explains the theoretical basis of our simulation.
2) We clarify this claim to simply note that we do not see a particular reason why we should expect any fundamental distinctions between the Ising and Fibonacci anyons, and that our methods could equally well be used to investigate alternative noise models if desired.
3) We agree that this statement was vague, and so we soften it to simply note that we do not expect our threshold estimates to be particularly biased by the effect under consideration, as well as clarifying the surrounding discussion.
4) We clarify the language to make it clear that we only find evidence for a threshold, rather than prove its existence, and that it is the existence of the threshold which would imply the asymptotically perfect storage of quantum information.

@@

Referee B:

We thank the referee for their thoughtful comments on our manuscript. Though the referee is of the opinion that our present work is incremental and of restricted interest, we believe that the ability to simulate error-correction in universal anyon models is a key development in the study of topological quantum computation. While previous analogous calculations for non-universal nonabelian anyon codes are superficially similar, the structure of the present simulations is significantly different and even the possibility of performing such a simulation may have been previously regarded as intractable. We hope that the extended discussion of the simulation algorithm provided in the supplementary material will demonstrate the novel approach we have taken to this problem, as compared to our previous work.
Since universal nonabelian anyons (and Fibonacci anyons in particular) are being pursued in many diverse experimental architectures for the purpose of topological quantum computation, we believe that the ability to numerically benchmark topological error-correction protocols will have a significant impact on the field.

In response to the referee's specific concerns:

@@

- We have expanded the discussion of the measure of memory lifetime used, and how it compares to iid noise strength (in particular noting that when comparable, the discrepancy would be of the order of 10% of the value for the kinds of lifetimes we consider). We also clarify the abstract to make it clear that the quoted threshold is given in terms of average errors per edge.

- We agree that in principle, given a sufficiently low physical error rate in a topological system, conventional quantum codes and error-correction techniques could be used to provide error-correction of a topological qubit. However, this would fail to exploit the inherent protection provided by the topological nature of the system. Most protocols for fault-tolerant quantum computation are motivated precisely by the lack of a need to perform standard fault-tolerant quantum circuity constructions since the topological features can be exploited to provide protection. We demonstrate how to simulate these schemes.

- We have noted that our analysis applies to both continuum and lattice systems with anyonic excitations, including several experimental systems such as fractional quantum Hall systems, lattice spin models, and composite heterostructures. Obviously, the experimental details of an implementation of our error-correction protocol would vary significantly from architecture to architecture, but our protocol only makes use of basic topological operations (such as joint charge measurements and charge transport) which are natural in any system where anyonic excitations arise. Since more precide descriptions of how to implement these operations (such as a circuit description) would unecessarily require restricting to a single experimental setup, we intentionally leave this question for future work. Our noise model is similarly vague but flexible, again accounting for sources of noise that are expected from generic topological systems with a mass gap, such as thermal excitations or stray fields. Again, if an analysis for a specific experimental apparatus were desired, our methods could be tailored to such a setting. We note as an open question tailoring our simulation to "realistic" microscopic lattice models, for example.

- While equations 1 and 2 may seem imprecise due to their graphical presentation, they are actually a precise representation of the corresponding topological processes. Due to space constraints, we have not been able to expand on this notation to the desired degree, but we have attempted to clarify this slightly, and provided a reference to a new manuscript where this presentation of topological operations is discussed in more detail. We have also explained the origin of the topological degeneracy as a flux through the non-trivial loop of the manifold.

@@

- We hope that the more extensive discussion of the error-correction protocol and simulation algorithm provided in the supplementary material clarifies the terse description in the main text.

- We have clarified this remark.

- We agree that this was poorly phrased, and have removed this remark. Our intention was merely to note that our reasoning for expecting the simulations to be efficient was of course an asymptotic argument, and that in the finite systems we study, we are nevertheless able to simulate in situations which could fall outside these nice cases, up to the lattice sizes shown.

@@

- In response to another comment we have removed this argument. What we had meant was the error-correction protocol failing to return to the codespace.

Summary of main changes made:
- In abstract, clarified the error-correction threshold quoted
- Added a note about physical systems that our work applies to
- Cite the new manuscript arXiv:1610.05384 that includes more detailed discussion of the representation of topological operations used, and how it relates to our simulation algorithm
- Described the origin of the topological degeneracy as a flux through the torus
- Expanded the discussion of our justification for presenting pair-creation-only results
- Expanded the discussion of the measure of noise strength useed
- Added supplementary materials greatly expanding on the details of the simulation algorithm

### 2016-10-25 resubmit/main text/fib2.tex
resubmitted

%\usepackage{epstopdf} % to include .eps graphics files with pdfLaTeX

@@

In order to efficiently classically simulate an error-correction protocol for 
a topologically ordered quantum memory, it is necessary to simulate 
the physical noise processes, the decoding algorithm, and the physical recovery operations. 
Decoding algorithms are typically designed to run efficiently on a 
classical computer, but there is generally no guarantee that the 
noise and recovery processes should be classically simulable.
Because of this, almost all of the sizable research effort 
on active quantum error correction for topological systems has focused 
on the case of abelian anyons~\cite{Dennis2002, Duclos-Cianci2010, Duclos-Cianci2010a, Wang2010, Wang2010a, Duclos-Cianci2013, Bravyi2011, Bombin2012, Wootton2012, Anwar2014, Watson2014, Hutter2014a, Bravyi2014, Wootton2015, Fowler2015, Andrist2015}, which can be efficiently simulated due to the fact that they cannot be used for quantum computation.
%Systems of abelian anyons are well suited to studying quantum 
%error correction because (at the RG fixed point) noise and 
%recovery processes can be efficiently simulated numerically, allowing lattice simulations 
%of decoding with over 1 million sites~\cite{Duclos-Cianci2010}. 
%Standard algorithms are specifically tailored to exploit the abelian nature 
%of these particles, particularly that abelian anyons cannot be used for quantum computation.

@@

We consider a 
2-dimensional system with
point-like anyonic quasiparticle excitations.%, which exhibit exotic statistics under exchange.
The worldlines of these particles form \emph{braids}
in (2+1)-dimensions
which act unitarily on the Hilbert space of degrees of freedom known as the \emph{fusion space}.
This space is associated with
the topological observables of the system: these
are total charge measurements within regions bounded by 
closed loops.% (Wilson loops).
The possible results of such a charge measurement correspond to different anyon particle types in the model.
These dynamics and observables obey algebraic rules
given by a unitary modular tensor category~\cite{Wang2010b}. In contrast to the approach often taken, we consider the topological observables, rather than the anyons themselves, to be affected by braiding processes (see \Fref{f:braidloop}).
%From the perspective of
%\emph{topological quantum field theory},
%anyons are modeled
%as punctures in a surface~\cite{Pfeifer2014}, 
%and the observables, rather than the anyons themselves, are considered to be deformed by braiding processes (see \Fref{f:braidloop}).
%and it is not
%the anyons themselves that braid,
%but the manifold in which the anyons reside 
%that becomes deformed (twisted) by these braid moves.
%This is the perspective we adopt (see \Fref{f:braidloop}).

\begin{figure}[t!]
\begin{center}
    \includegraphics[]{pic-braid-loop.pdf}
\caption{
The deformation of observables corresponding to the implementation of a braid process on three anyons is shown. Configurations before and after are connected by world lines shown in red, while the charge observables are shown in black.
This process relates two different ways of fusing the top two charges.
%In general, braiding will twist these loops in different ways following
%the deformation of the manifold itself.
\label{f:braidloop}
}
\end{center}
\vspace{-10pt}
\end{figure}

The defining difference between abelian and nonabelian
anyon theories is that in an abelian theory particle content alone uniquely determines the outcome of joint charge measurements.
In contrast, outcomes for nonabelian charge measurements depend on the history of the particles as well as their type.
%That is, the fusion space is one-dimensional for abelian anyons, and generally larger for nonabelian anyons.
We consider a system supporting nonabelian Fibonacci
anyon excitations, denoted by $\tau$.
Two such anyons can have total charge
that is either $\tau$ or $\vac$ (vacuum), or any superposition of these, and
so the fusion space in this case is 2-dimensional.
We can represent basis states for this space using diagrams 
of definite total charge for the Wilson loops, 
and arbitrary states as linear combinations of these diagrams:
\begin{align*}
\includegraphics[]{pic-fibonacci.pdf}
\end{align*}
%For $n$ anyons of type $\tau$, the 
%dimension of the fusion space grows asymptotically as $\varphi^n$, where $\varphi=\frac{1+\sqrt{5}}{2}$ 
%is the golden ratio.

Observables associated to non-intersecting loops commute, and so
a basis for the space can be built from a maximal
set of disjoint, nested loops.
For three anyons, two
possible ways of nesting loops are related
via $F$-moves:
\begin{align}
\label{e:fmove}
\includegraphics[]{pic-fmove.pdf}
\end{align}
Here we have shown particles with charges $a$, $b$, and $c$
as well as total charge $d$.
The lefthand side shows a state where the anyons with charge $a$ and $b$ are
observed to have total charge $i$.
The righthand side involves a superposition 
over total charge $j$ of the anyons with charge $b$ and $c$. 
The green line serves to linearly
order the anyons, and track
%deformations in the underlying space, 
%i.e.\ 
the history of braiding processes (see Ref.~\cite{Burton2016} for a more comprehensive discussion).
%It also denotes the direction along which $F$-moves occur. 
A clockwise braiding process, or \emph{half-twist}, is effected by an $R$-move:
\begin{align}
\label{e:rmove}
\includegraphics[]{pic-rmove.pdf}
\end{align}

@@

Pair-creation events acting within a single tile do not affect the corresponding observable, and so the only pair-creation events we need explicitly consider act between neighboring pairs of tiles. These are then each associated with an edge of the lattice $\Lambda$, chosen 
uniformly at random to model high-temperature, short timescale thermalizing dynamics.
In studies of codes based on abelian anyon models, the error correction threshold or memory lifetime is typically quoted in terms of an iid noise strength per edge. This measure is not appropriate in a nonabelian anyon setting, where noise processes on neighbouring edges do not commute. We thus measure the error correction threshold and memory lifetime in terms of the average number of noise processes per edge. 
It is easy to see that, in those cases where they are both appropriate, these two methods coincide in the limit of low error rates, and for the typical noise strengths we encounter in this paper, the discrepancy is around $10\%$ (see Ref.~\cite{Brell2013} for more details). 
%The thresholds we consider in this paper are on the order of $0.1$ noise processes per edge. In models where both noise strength measures are appropriate, such as the toric code under bit-flip errors, the discrepancy between the two values is around $10\%$ at these strengths.

We consider this treatment of anyon dynamics to be a phenomenological model in that
it neglects any microscopic details of the system.
This is consistent with the principles of topologically 
ordered systems and anyonic physics, where the key universal features describing the 
anyon model correspond to large length-scale physics, while the microscopic physics plays 
a less important (and non-universal) role. Note also that our analysis applies equally well to either a continuum setting, or to discrete lattice models supporting anyonic excitations.
%Additionally, while we model a continuum anyon theory, our analysis can be trivially reinterpreted to apply directly to lattice spin models or other systems where space is fundamentally discrete.

@@

Note that unlike the case of abelian anyons, the decoder
cannot determine the charge of each cluster given only the syndrome information (as in \cite{Bravyi2011}),
and so must repeatedly physically query the system to measure these charges.
%This is also in contrast to abstract quantum codes, where syndrome extraction can typically be performed in one step.
Our simulation proceeds in this way as a dialogue between decoder
and system, terminating when either the decoder itself terminates or 
when it performs a homologically nontrivial operation, thereby performing a potential logical error.
%altering the 
%codespace (and failing to perform successful recovery).
%Note that, as was found in Ref.~\cite{Brell2013}, we expect that 
%our qualitative results may be reproduced by most alternative families 
%of decoders, although it may not be clear in all cases how to extend these decoders to the nonabelian setting.
%The advantage of using a clustering decoder is 
%its simplicity and flexibility, and the fact that its clustering 
%scheme is compatible with the structure in the noise 
%processes that allows us to classically simulate them.

@@

In the regime where the combined action of noise and error-correction does not percolate
it is reasonable to expect that the simulation is efficient.
However, with strong enough noise the state in the fusion space will
no longer decompose at all and computing dynamics will
become exponentially difficult in the system size.
%Despite this, we use heuristics 
%that minimize braid moves, which helps to
%track the state beyond the
%sub-percolated regime.
%This enables simulation of error correction in
Nevertheless, we are able to simulate error-correction in
the regime around the error-correction threshold for linear lattice sizes up to $L=128$.

@@

In order to track the state of the system we represent the state of the fusion space with 
a set of disjoint directed curves, 
one for each connected component with trivial total charge.
Unlike previous work~\cite{Brell2013}, this creates a dynamically generated basis for the fusion space 
that allows for tensor factorization of disjoint components.
A pair-creation noise process corresponds to the 
addition of an extra curve to the lattice, supporting
two new anyons.
Following the noise processes, our simulation must 
measure the total charge within each tile; the results of 
these measurements will form the error syndrome. 
This requires joining the curves that intersect that tile, 
and then performing $R$- and $F$-moves on the resulting
curve so that 
all anyons within the tile have been 
localized within a contiguous region of the curve. 
An example of this 
procedure for a simple noise process is shown in \Fref{f:syndrome}.
This procedure is discussed in more detail in the supplementary material, and the theoretical framework underlying it is expanded in Ref.~\cite{CurveDiagrams}.
%The details of the algorithm and data structures used for 
%this procedure will be discussed elsewhere.
Braiding processes that encircle 
a non-trivial loop of our (toric) manifold can also be 
treated in an analogous way, following e.g.~\cite{Pfeifer2012}.

@@

We can guarantee that error-correction will succeed whenever
the action of noise plus decoder 
does not percolate the anyons over the lattice,
but it is possible that percolated events may still result in no error. 
The connection between the percolation threshold and the error-correction threshold 
is not well understood in general~\cite{Hastings2014}, though it is clear 
that our threshold estimate would be a lower bound for 
the true threshold that may be found if all events 
(including those that have percolated) were simulated. 
In any case, we do not expect this possible discrepancy to be significant in our simulations.
%However, naively computing the effect of the simplest possible homologically nontrivial operations consistently yields either a logical error or a complete failure to return to the codespace (see \Aref{s:homnontrivial}). As such it seems reasonable to suggest that neglecting the full simulation of 
%these events does not significantly affect our observed threshold value.

@@

There are several interesting avenues for further research. 
Although it is not completely obvious how to do so, 
applying similar methods to more realistic models such as concrete 
microscopic spin models or models with non-topological features would give 
direct insight into practical error rates needed for nonabelian topological quantum memories.% in nonabelian systems. 
It would also be interesting to find \emph{classical} spin models 
whose phase diagram encodes the threshold for error correction in these systems~\cite{Dennis2002}.
Finally, an important extension of this work would be to the simulation of \emph{fault-tolerant} error-correction protocols for nonabelian anyon codes.

%------------------------------------------------------------------------------------------------------------%
\acknowledgments

@@

\bibliography{refs2}

>>>>

@@

In order to efficiently classically simulate an error-correction protocol for 
a topologically ordered quantum memory, it is necessary to simulate 
the physical noise processes, the decoding algorithm, and the physical recovery operations. 
Decoding algorithms are typically designed to run efficiently on a 
classical computer, but there is generally no guarantee that the 
noise and recovery processes should be classically simulable.
Because of this, almost all of the sizable research effort 
on active quantum error correction for topological systems has focused 
on the case of abelian anyons~\cite{Dennis2002, Duclos-Cianci2010, Duclos-Cianci2010a, Wang2010, Wang2010a, Duclos-Cianci2013, Bravyi2011, Bombin2012, Wootton2012, Anwar2014, Watson2014, Hutter2014a, Bravyi2014, Wootton2015, Fowler2015, Andrist2015}, which can be efficiently simulated due to the fact that they cannot be used for quantum computation.

@@

We consider a 
2-dimensional system with
point-like anyonic quasiparticle excitations.
The worldlines of these particles form \emph{braids}
in (2+1)-dimensions
which act unitarily on the Hilbert space of degrees of freedom known as the \emph{fusion space}.
This space is associated with
the topological observables of the system: these
are total charge measurements within regions bounded by 
closed loops.
The possible results of such a charge measurement correspond to different anyon particle types in the model.
These dynamics and observables obey algebraic rules
given by a unitary modular tensor category~\cite{Wang2010b}. In contrast to the approach often taken, we consider the topological observables, rather than the anyons themselves, to be affected by braiding processes (see \Fref{f:braidloop}).

\begin{figure}[t!]
\begin{center}
    \includegraphics[]{pic-braid-loop.pdf}
\caption{
The deformation of observables corresponding to the implementation of a braid process on three anyons is shown. Configurations before and after are connected by world lines shown in red, while the charge observables are shown in black.
This process relates two different ways of fusing the top two charges.
\label{f:braidloop}
}
\end{center}
\vspace{-10pt}
\end{figure}

The defining difference between abelian and nonabelian
anyon theories is that in an abelian theory particle content alone uniquely determines the outcome of joint charge measurements.
In contrast, outcomes for nonabelian charge measurements depend on the history of the particles as well as their type.

We consider a system supporting nonabelian Fibonacci
anyon excitations, denoted by $\tau$.
Two such anyons can have total charge
that is either $\tau$ or $\vac$ (vacuum), or any superposition of these, and
so the fusion space in this case is 2-dimensional.
We can represent basis states for this space using diagrams 
of definite total charge for the Wilson loops, 
and arbitrary states as linear combinations of these diagrams:
\begin{align*}
\includegraphics[]{pic-fibonacci.pdf}
\end{align*}

Observables associated to non-intersecting loops commute, and so
a basis for the space can be built from a maximal
set of disjoint, nested loops.
For three anyons, two
possible ways of nesting loops are related
via $F$-moves:
\begin{align}
\label{e:fmove}
\includegraphics[]{pic-fmove.pdf}
\end{align}
Here we have shown particles with charges $a$, $b$, and $c$
as well as total charge $d$.
The lefthand side shows a state where the anyons with charge $a$ and $b$ are
observed to have total charge $i$.
The righthand side involves a superposition 
over total charge $j$ of the anyons with charge $b$ and $c$. 
The green line serves to linearly
order the anyons, and track
the history of braiding processes (see Ref.~\cite{Burton2016} for a more comprehensive discussion).
A clockwise braiding process, or \emph{half-twist}, is effected by an $R$-move:
\begin{align}
\label{e:rmove}
\includegraphics[]{pic-rmove.pdf}
\end{align}

@@

Pair-creation events acting within a single tile do not affect the corresponding observable, and so the only pair-creation events we need explicitly consider act between neighboring pairs of tiles. These are then each associated with an edge of the lattice $\Lambda$, chosen 
uniformly at random to model high-temperature, short timescale thermalizing dynamics.
In studies of codes based on abelian anyon models, the error correction threshold or memory lifetime is typically quoted in terms of an iid noise strength per edge. This measure is not appropriate in a nonabelian anyon setting, where noise processes on neighbouring edges do not commute. We thus measure the error correction threshold and memory lifetime in terms of the average number of noise processes per edge. 
It is easy to see that, in those cases where they are both appropriate, these two methods coincide in the limit of low error rates, and for the typical noise strengths we encounter in this paper, the discrepancy is around $10\%$ (see Ref.~\cite{Brell2013} for more details).

We consider this treatment of anyon dynamics to be a phenomenological model in that
it neglects any microscopic details of the system.
This is consistent with the principles of topologically 
ordered systems and anyonic physics, where the key universal features describing the 
anyon model correspond to large length-scale physics, while the microscopic physics plays 
a less important (and non-universal) role. Note also that our analysis applies equally well to either a continuum setting, or to discrete lattice models supporting anyonic excitations.

@@

Note that unlike the case of abelian anyons, the decoder
cannot determine the charge of each cluster given only the syndrome information (as in \cite{Bravyi2011}),
and so must repeatedly physically query the system to measure these charges.
Our simulation proceeds in this way as a dialogue between decoder
and system, terminating when either the decoder itself terminates or 
when it performs a homologically nontrivial operation, thereby performing a potential logical error.

@@

In the regime where the combined action of noise and error-correction does not percolate
it is reasonable to expect that the simulation is efficient.
However, with strong enough noise the state in the fusion space will
no longer decompose at all and computing dynamics will
become exponentially difficult in the system size.
Nevertheless, we are able to simulate error-correction in
the regime around the error-correction threshold for linear lattice sizes up to $L=128$.

@@

In order to track the state of the system we represent the state of the fusion space with 
a set of disjoint directed curves, 
one for each connected component with trivial total charge.
Unlike previous work~\cite{Brell2013}, this creates a dynamically generated basis for the fusion space 
that allows for tensor factorization of disjoint components.
A pair-creation noise process corresponds to the 
addition of an extra curve to the lattice, supporting
two new anyons.
Following the noise processes, our simulation must 
measure the total charge within each tile; the results of 
these measurements will form the error syndrome. 
This requires joining the curves that intersect that tile, 
and then performing $R$- and $F$-moves on the resulting
curve so that 
all anyons within the tile have been 
localized within a contiguous region of the curve. 
An example of this 
procedure for a simple noise process is shown in \Fref{f:syndrome}.
This procedure is discussed in more detail in the supplementary material, and the theoretical framework underlying it is expanded in Ref.~\cite{Burton2016}.
Braiding processes that encircle 
a non-trivial loop of our (toric) manifold can also be 
treated in an analogous way, following e.g.~\cite{Pfeifer2012}.

@@

We can guarantee that error-correction will succeed whenever
the action of noise plus decoder 
does not percolate the anyons over the lattice,
but it is possible that percolated events may still result in no error. 
The connection between the percolation threshold and the error-correction threshold 
is not well understood in general~\cite{Hastings2014}, though it is clear 
that our threshold estimate would be a lower bound for 
the true threshold that may be found if all events 
(including those that have percolated) were simulated. 
In any case, we do not expect this possible discrepancy to be significant in our simulations.

@@

There are several interesting avenues for further research. 
Although it is not completely obvious how to do so, 
applying similar methods to more realistic models such as concrete 
microscopic spin models or models with non-topological features would give 
direct insight into practical error rates needed for nonabelian topological quantum memories.
It would also be interesting to find \emph{classical} spin models 
whose phase diagram encodes the threshold for error correction in these systems~\cite{Dennis2002}.
Finally, an important extension of this work would be to the simulation of \emph{fault-tolerant} error-correction protocols for nonabelian anyon codes.

%------------------------------------------------------------------------------------------------------------%
\begin{acknowledgments}

@@

\end{acknowledgments}

%merlin.mbs apsrev4-1.bst 2010-07-25 4.21a (PWD, AO, DPC) hacked
%Control: key (0)
%Control: author (8) initials jnrlst
%Control: editor formatted (1) identically to author
%Control: production of article title (-1) disabled
%Control: page (0) single
%Control: year (1) truncated
%Control: production of eprint (0) enabled
\begin{thebibliography}{42}%
\makeatletter
\providecommand \@ifxundefined [1]{%
 \@ifx{#1\undefined}
}%
\providecommand \@ifnum [1]{%
 \ifnum #1\expandafter \@firstoftwo
 \else \expandafter \@secondoftwo
 \fi
}%
\providecommand \@ifx [1]{%
 \ifx #1\expandafter \@firstoftwo
 \else \expandafter \@secondoftwo
 \fi
}%
\providecommand \natexlab [1]{#1}%
\providecommand \enquote  [1]{``#1''}%
\providecommand \bibnamefont  [1]{#1}%
\providecommand \bibfnamefont [1]{#1}%
\providecommand \citenamefont [1]{#1}%
\providecommand \href@noop [0]{\@secondoftwo}%
\providecommand \href [0]{\begingroup \@sanitize@url \@href}%
\providecommand \@href[1]{\@@startlink{#1}\@@href}%
\providecommand \@@href[1]{\endgroup#1\@@endlink}%
\providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
  `\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
\providecommand \@@startlink[1]{}%
\providecommand \@@endlink[0]{}%
\providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
\providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
\providecommand \urlprefix  [0]{URL }%
\providecommand \Eprint [0]{\href }%
\providecommand \doibase [0]{http://dx.doi.org/}%
\providecommand \selectlanguage [0]{\@gobble}%
\providecommand \bibinfo  [0]{\@secondoftwo}%
\providecommand \bibfield  [0]{\@secondoftwo}%
\providecommand \translation [1]{[#1]}%
\providecommand \BibitemOpen [0]{}%
\providecommand \bibitemStop [0]{}%
\providecommand \bibitemNoStop [0]{.\EOS\space}%
\providecommand \EOS [0]{\spacefactor3000\relax}%
\providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
\let\auto@bib@innerbib\@empty
%</preamble>
\bibitem [{\citenamefont {Kitaev}(2003)}]{Kitaev2003}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~Y.}\ \bibnamefont
  {Kitaev}},\ }\href {\doibase 10.1016/S0003-4916(02)00018-0} {\bibfield
  {journal} {\bibinfo  {journal} {Ann. Phys.}\ }\textbf {\bibinfo {volume}
  {303}},\ \bibinfo {pages} {2} (\bibinfo {year} {2003})},\ \Eprint
  {http://arxiv.org/abs/quant-ph/9707021} {arXiv:quant-ph/9707021} \BibitemShut
  {NoStop}%
\bibitem [{\citenamefont {Dennis}\ \emph {et~al.}(2002)\citenamefont {Dennis},
  \citenamefont {Kitaev}, \citenamefont {Landahl},\ and\ \citenamefont
  {Preskill}}]{Dennis2002}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
  {Dennis}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Kitaev}},
  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Landahl}}, \ and\
  \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Preskill}},\ }\href
  {\doibase 10.1063/1.1499754} {\bibfield  {journal} {\bibinfo  {journal} {J.
  Math. Phys.}\ }\textbf {\bibinfo {volume} {43}},\ \bibinfo {pages} {4452}
  (\bibinfo {year} {2002})},\ \Eprint {http://arxiv.org/abs/quant-ph/0110143}
  {arXiv:quant-ph/0110143} \BibitemShut {NoStop}%
\bibitem [{\citenamefont {Nayak}\ \emph {et~al.}(2008)\citenamefont {Nayak},
  \citenamefont {Simon}, \citenamefont {Stern}, \citenamefont {Freedman},\ and\
  \citenamefont {Das~Sarma}}]{Nayak2008}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
  {Nayak}}, \bibinfo {author} {\bibfnamefont {S.~H.}\ \bibnamefont {Simon}},
  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Stern}}, \bibinfo
  {author} {\bibfnamefont {M.}~\bibnamefont {Freedman}}, \ and\ \bibinfo
  {author} {\bibfnamefont {S.}~\bibnamefont {Das~Sarma}},\ }\href {\doibase
  10.1103/RevModPhys.80.1083} {\bibfield  {journal} {\bibinfo  {journal} {Rev.
  Mod. Phys.}\ }\textbf {\bibinfo {volume} {80}},\ \bibinfo {pages} {1083}
  (\bibinfo {year} {2008})},\ \Eprint {http://arxiv.org/abs/0707.1889}
  {arXiv:0707.1889} \BibitemShut {NoStop}%
\bibitem [{\citenamefont {Bravyi}\ \emph {et~al.}(2010)\citenamefont {Bravyi},
  \citenamefont {Hastings},\ and\ \citenamefont {Michalakis}}]{Bravyi2010}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
  {Bravyi}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Hastings}}, \
  and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Michalakis}},\
  }\href {\doibase 10.1063/1.3490195} {\bibfield  {journal} {\bibinfo
  {journal} {J. Math. Phys.}\ }\textbf {\bibinfo {volume} {51}},\ \bibinfo
  {pages} {093512} (\bibinfo {year} {2010})},\ \Eprint
  {http://arxiv.org/abs/1001.0344} {arXiv:1001.0344} \BibitemShut {NoStop}%
\bibitem [{\citenamefont {Bravyi}\ and\ \citenamefont
  {Hastings}(2011)}]{Bravyi2011a}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
  {Bravyi}}\ and\ \bibinfo {author} {\bibfnamefont {M.~B.}\ \bibnamefont
  {Hastings}},\ }\href {\doibase 10.1007/s00220-011-1346-2} {\bibfield
  {journal} {\bibinfo  {journal} {Comm. Math. Phys.}\ }\textbf {\bibinfo
  {volume} {307}},\ \bibinfo {pages} {609} (\bibinfo {year} {2011})},\ \Eprint
  {http://arxiv.org/abs/arXiv:1001.4363} {arXiv:1001.4363} \BibitemShut
  {NoStop}%
\bibitem [{\citenamefont {Michalakis}\ and\ \citenamefont
  {Zwolak}(2013)}]{Michalakis2013}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
  {Michalakis}}\ and\ \bibinfo {author} {\bibfnamefont {J.~P.}\ \bibnamefont
  {Zwolak}},\ }\href {\doibase 10.1007/s00220-013-1762-6} {\bibfield  {journal}
  {\bibinfo  {journal} {Comm. Math. Phys.}\ }\textbf {\bibinfo {volume}
  {322}},\ \bibinfo {pages} {277} (\bibinfo {year} {2013})},\ \Eprint
  {http://arxiv.org/abs/1109.1588} {arXiv:1109.1588} \BibitemShut {NoStop}%
\bibitem [{\citenamefont {Wilczek}(1990)}]{Wilczek1990}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
  {Wilczek}},\ }\href@noop {} {\emph {\bibinfo {title} {Fractional Statistics
  and Anyon Superconductivity}}}\ (\bibinfo  {publisher} {World Scientific},\
  \bibinfo {address} {Singapore},\ \bibinfo {year} {1990})\BibitemShut
  {NoStop}%
\bibitem [{\citenamefont {Freedman}\ \emph {et~al.}(2002)\citenamefont
  {Freedman}, \citenamefont {Larsen},\ and\ \citenamefont
  {Wang}}]{Freedman2002}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~H.}\ \bibnamefont
  {Freedman}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Larsen}}, \
  and\ \bibinfo {author} {\bibfnamefont {Z.}~\bibnamefont {Wang}},\ }\href
  {\doibase 10.1007/s002200200645} {\bibfield  {journal} {\bibinfo  {journal}
  {Comm. Math. Phys.}\ }\textbf {\bibinfo {volume} {227}},\ \bibinfo {pages}
  {605} (\bibinfo {year} {2002})},\ \Eprint
  {http://arxiv.org/abs/quant-ph/0001108} {arXiv:quant-ph/0001108} \BibitemShut
  {NoStop}%
\bibitem [{\citenamefont {Pastawski}\ \emph {et~al.}(2010)\citenamefont
  {Pastawski}, \citenamefont {Kay}, \citenamefont {Schuch},\ and\ \citenamefont
  {Cirac}}]{Pastawski2010}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
  {Pastawski}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Kay}},
  \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont {Schuch}}, \ and\ \bibinfo
  {author} {\bibfnamefont {J.~I.}\ \bibnamefont {Cirac}},\ }\href@noop {}
  {\bibfield  {journal} {\bibinfo  {journal} {Quant. Inf. Comput.}\ }\textbf
  {\bibinfo {volume} {10}},\ \bibinfo {pages} {580} (\bibinfo {year} {2010})},\
  \Eprint {http://arxiv.org/abs/0911.3843} {arXiv:0911.3843} \BibitemShut
  {NoStop}%
\bibitem [{\citenamefont {Duclos-Cianci}\ and\ \citenamefont
  {Poulin}(2010{\natexlab{a}})}]{Duclos-Cianci2010}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
  {Duclos-Cianci}}\ and\ \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
  {Poulin}},\ }\href {\doibase 10.1103/PhysRevLett.104.050504} {\bibfield
  {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo
  {volume} {104}},\ \bibinfo {pages} {050504} (\bibinfo {year}
  {2010}{\natexlab{a}})},\ \Eprint {http://arxiv.org/abs/0911.0581}
  {arXiv:0911.0581} \BibitemShut {NoStop}%
\bibitem [{\citenamefont {Duclos-Cianci}\ and\ \citenamefont
  {Poulin}(2010{\natexlab{b}})}]{Duclos-Cianci2010a}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
  {Duclos-Cianci}}\ and\ \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
  {Poulin}},\ }in\ \href {\doibase 10.1109/CIG.2010.5592866} {\emph {\bibinfo
  {booktitle} {Information Theory Workshop (ITW), 2010 IEEE}}}\ (\bibinfo
  {year} {2010})\ pp.\ \bibinfo {pages} {1--5},\ \Eprint
  {http://arxiv.org/abs/1006.1362} {arXiv:1006.1362} \BibitemShut {NoStop}%
\bibitem [{\citenamefont {Wang}\ \emph
  {et~al.}(2010{\natexlab{a}})\citenamefont {Wang}, \citenamefont {Fowler},
  \citenamefont {Stephens},\ and\ \citenamefont {Hollenberg}}]{Wang2010}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.~S.}\ \bibnamefont
